Job Demands-Resources model components through the lens of O*NET classifications

### 2022-11-11 Submission.Rmd
porting Word document notes into .Rmd

abstract: |
  O\*NET work characteristics were rated in terms of relevance, perception as a demand, and perception as a resource. All the results of this current study match the stress-appraisal stuff. Next steps: 1) discuss results within stress-appraisal framework (Lazarus & Bookman), 2) different literature on challenge and hindrance demands. Job Demands Resources theory that says resources and demands are relatively universal is NOT consistent with these findings. JDR neglects the other 2 literatures. Analytically pull O*Net descriptors that reflect universal demands/resources (e.g., autonomy) and see how much variability there is on those. Maybe forget about cross-walk thing. May actually want to start with this: https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit#gid=1041061499.

@@

Given the popularity of the Job Demands-Resources Theory [JD-R; @demerouti2001job] in exploring questions related to everything from motivation to job design, we aim to explore the intersection between *perceptions* of job demands and resources, and the broad set of job characteristics provided on O\*Net. This project makes three contributions. We aim to first explore whether ratings of of O\*Net item groupings align with the stated "resources" and "demands" presented in the job demands-resources theory. We then present evidence documenting whether O\*Net job and task descriptors are similarly rated as resources, challenge- or hindrance demands, and lastly, whether such ratings differ across job categories/classifications. 
Across two studies, a series of evaluations were made that used: 1) direct O\*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance of different types of workers. Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O\*Net is provided.

## The Job demands-Resources Theory

The overarching context for this study is that of the job demands-resources theory, which is an expansion of the well-studied job demands-resources model [@demerouti2001job]. One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands. *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job]. In contrast, *demands* include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; @demerouti2001job). 
Cognitively, the perception of an element of ones job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation [resulting from resources; @bakker2014job]. Pertinent to the current study, demanding job characteristics are frequently associated with negative outcomes [e.g., @bakker2003dual], whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation [@bakker2007job].

## Objective vs. Subjective Nature of Demands and Resources: The Role of Appraisal

@@

# Study 1

@@

```{r scale-level-graphs eval = FALSE}
#this is a placeholder for the scale level faceted graph found in plotscript_practice script file. 
```

>>>>

abstract: |
  O\*NET work characteristics were rated in terms of relevance, perception as a demand, and perception as a resource. All the results of this current study match the stress-appraisal stuff. Next steps: 1) discuss results within stress-appraisal framework (Lazarus & Bookman), 2) different literature on challenge and hindrance demands. Job Demands Resources theory that says resources and demands are relatively universal is NOT consistent with these findings. JDR neglects the other 2 literatures. Analytically pull O*Net descriptors that reflect universal demands/resources (e.g., autonomy) and see how much variability there is on those. Maybe forget about cross-walk thing. May actually want to start with this: https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit#gid=1041061499.[^foot1]

@@

[^foot1]: Need to rewrite

Given the popularity of the Job Demands-Resources Theory [JD-R; @demerouti2001job] in exploring questions related to everything from motivation to job design, we aim to explore the intersection between *perceptions* of job demands and resources, and the broad set of job characteristics provided on O\*Net. This project makes three contributions. We aim to first explore whether ratings of of O\*Net item groupings align with the stated "resources" and "demands" presented in the job demands-resources theory. We then present evidence documenting whether O\*Net job and task descriptors are similarly rated as resources, challenge- or hindrance demands, and lastly, whether such ratings differ across job categories/classifications.

Across two studies, a series of evaluations were made that used: 1) direct O\*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance of different types of workers. Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O\*Net is provided.

## The Job demands-Resources Theory[^foot2]

[^foot2]: Need to expand this section

The overarching context for this study is that of the job demands-resources theory, which is an expansion of the well-studied job demands-resources model [@demerouti2001job]. One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands. *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job]. In contrast, *demands* include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; @demerouti2001job).

Cognitively, the perception of an element of ones job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation [resulting from resources; @bakker2014job]. Pertinent to the current study, demanding job characteristics are frequently associated with negative outcomes [e.g., @bakker2003dual], whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation [@bakker2007job].

**Add information on Challenge-Hindrance stuff - it's in the SIOP submission so should be able to copy/paste**

## Objective vs. Subjective Nature of Demands and Resources: The Role of Appraisal[^foot3]

[^foot3]: Look for more recent literature - this is currently a bit dated

@@

# Study 1[^foot4]

[^foot4]: Need to delete all references to Study 1 and Study 2

@@

```{r scale-level-graphs, eval = FALSE}
#this is a placeholder for the scale level faceted graph found in plotscript_practice script file. 
```

### 2022-11-11 Submission.tex
porting Word document notes into .Rmd

\abstract{%
O*NET work characteristics were rated in terms of relevance, perception as a demand, and perception as a resource. All the results of this current study match the stress-appraisal stuff. Next steps: 1) discuss results within stress-appraisal framework (Lazarus \& Bookman), 2) different literature on challenge and hindrance demands. Job Demands Resources theory that says resources and demands are relatively universal is NOT consistent with these findings. JDR neglects the other 2 literatures. Analytically pull O*Net descriptors that reflect universal demands/resources (e.g., autonomy) and see how much variability there is on those. Maybe forget about cross-walk thing. May actually want to start with this: \url{https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit\#gid=1041061499}.

@@

Given the popularity of the Job Demands-Resources Theory {[}JD-R; Demerouti et al. (2001){]} in exploring questions related to everything from motivation to job design, we aim to explore the intersection between \emph{perceptions} of job demands and resources, and the broad set of job characteristics provided on O*Net. This project makes three contributions. We aim to first explore whether ratings of of O*Net item groupings align with the stated ``resources'' and ``demands'' presented in the job demands-resources theory. We then present evidence documenting whether O*Net job and task descriptors are similarly rated as resources, challenge- or hindrance demands, and lastly, whether such ratings differ across job categories/classifications.
Across two studies, a series of evaluations were made that used: 1) direct O*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance of different types of workers. Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O*Net is provided.

\hypertarget{the-job-demands-resources-theory}{%
\subsection{The Job demands-Resources Theory}\label{the-job-demands-resources-theory}}

The overarching context for this study is that of the job demands-resources theory, which is an expansion of the well-studied job demands-resources model (Demerouti et al., 2001). One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands. \emph{Resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001). In contrast, \emph{demands} include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; Demerouti et al. (2001)).
Cognitively, the perception of an element of ones job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation {[}resulting from resources; A. B. Bakker and Demerouti (2014){]}. Pertinent to the current study, demanding job characteristics are frequently associated with negative outcomes (e.g., A. Bakker et al., 2003), whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation (A. B. Bakker et al., 2007).

\hypertarget{objective-vs.-subjective-nature-of-demands-and-resources-the-role-of-appraisal}{%
\subsection{Objective vs.~Subjective Nature of Demands and Resources: The Role of Appraisal}\label{objective-vs.-subjective-nature-of-demands-and-resources-the-role-of-appraisal}}

@@

\hypertarget{study-1}{%
\section{Study 1}\label{study-1}}

@@

@@

Looked through

While Study 1 explored the above questions across jobs, Study 2 considers a potentially important moderator: job classification. There is a distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework depending on \emph{job classification}. In fact, a growing body of evidence suggests people may not universally experience job characteristics as challenges or hinderances (e.g., (A. B. Bakker \& Sanz-Vergel, 2013); (Cavanaugh et al., 2000); (Gerich, 2017); (Podsakoff et al., 2007); (Webster et al., 2011)). Thus, Study 2 focuses on a fourth question of interest.

\begin{quote}
\emph{Research Question 4}: Does the \textbf{type of work} reported explain variability in the categorization of work characteristics into challenges, hindrances, and resources?
\end{quote}

\hypertarget{materials-1}{%
\subsection{Materials}\label{materials-1}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.

@@

\leavevmode\vadjust pre{\hypertarget{ref-podsakoff2007differential}{}}%
Podsakoff, N. P., LePine, J. A., \& LePine, M. A. (2007). Differential challenge stressor-hindrance stressor relationships with job attitudes, turnover intentions, turnover, and withdrawal behavior: A meta-analysis. \emph{Journal of Applied Psychology}, \emph{92}(2), 438.

@@

>>>>

\abstract{%
O*NET work characteristics were rated in terms of relevance, perception as a demand, and perception as a resource. All the results of this current study match the stress-appraisal stuff. Next steps: 1) discuss results within stress-appraisal framework (Lazarus \& Bookman), 2) different literature on challenge and hindrance demands. Job Demands Resources theory that says resources and demands are relatively universal is NOT consistent with these findings. JDR neglects the other 2 literatures. Analytically pull O*Net descriptors that reflect universal demands/resources (e.g., autonomy) and see how much variability there is on those. Maybe forget about cross-walk thing. May actually want to start with this: \url{https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit\#gid=1041061499}.\footnote{Need to rewrite}

@@

Given the popularity of the Job Demands-Resources Theory {[}JD-R; Demerouti et al. (2001){]} in exploring questions related to everything from motivation to job design, we aim to explore the intersection between \emph{perceptions} of job demands and resources, and the broad set of job characteristics provided on O*Net. This project makes three contributions. We aim to first explore whether ratings of of O*Net item groupings align with the stated ``resources'' and ``demands'' presented in the job demands-resources theory. We then present evidence documenting whether O*Net job and task descriptors are similarly rated as resources, challenge- or hindrance demands, and lastly, whether such ratings differ across job categories/classifications.

Across two studies, a series of evaluations were made that used: 1) direct O*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance of different types of workers. Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O*Net is provided.

\hypertarget{the-job-demands-resources-theoryfoot2}{%
\subsection[The Job demands-Resources Theory]{\texorpdfstring{The Job demands-Resources Theory\footnote{Need to expand this section}}{The Job demands-Resources Theory}}\label{the-job-demands-resources-theoryfoot2}}

The overarching context for this study is that of the job demands-resources theory, which is an expansion of the well-studied job demands-resources model (Demerouti et al., 2001). One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands. \emph{Resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001). In contrast, \emph{demands} include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; Demerouti et al. (2001)).

Cognitively, the perception of an element of ones job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation {[}resulting from resources; A. B. Bakker and Demerouti (2014){]}. Pertinent to the current study, demanding job characteristics are frequently associated with negative outcomes (e.g., A. Bakker et al., 2003), whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation (A. B. Bakker et al., 2007).

\textbf{Add information on Challenge-Hindrance stuff - it's in the SIOP submission so should be able to copy/paste}

\hypertarget{objective-vs.-subjective-nature-of-demands-and-resources-the-role-of-appraisalfoot3}{%
\subsection[Objective vs.~Subjective Nature of Demands and Resources: The Role of Appraisal]{\texorpdfstring{Objective vs.~Subjective Nature of Demands and Resources: The Role of Appraisal\footnote{Look for more recent literature - this is currently a bit dated}}{Objective vs.~Subjective Nature of Demands and Resources: The Role of Appraisal}}\label{objective-vs.-subjective-nature-of-demands-and-resources-the-role-of-appraisalfoot3}}

@@

\hypertarget{study-1foot4}{%
\section[Study 1]{\texorpdfstring{Study 1\footnote{Need to delete all references to Study 1 and Study 2}}{Study 1}}\label{study-1foot4}}

@@

\begin{quote}
Hypothesis 1: Job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
\end{quote}

\begin{quote}
Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.
\end{quote}

Add a description here of the exploratory stuff.

@@

@@

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-R-careless}{}}%
Yentes, R. D., \& Wilhelm, F. (2021). \emph{Careless: Procedures for computing indices of careless responding}.
